Methodology for Assessing the State of the Practice for Domain X

### 2020-06-12 StateOfPractice/Methodology/Methodology.tex
updated questionnaire section

\subsection{Task selection criteria}
**The task selection will be determined with the aid of the domain expert attached to any of the selected projects.\\ 
**The domain expert will be asked to consider the below criteria when defining a task. \\
**Domain experts will also be asked to identify what background knowledge is necessary for the suggested tasks - Novice, Intermediate, Advanced
\begin {enumerate}
\item Collectively all tasks should not take no more than 2 hours.
\item Selected tasks should reflect common use cases of  the software
\item Include tasks that require a set of sequential or hierarchical steps to be completed

\end {enumerate} 
\oo   {Are domain experts expected to provide step by step instructions to complete a tasks}

\subsection{Usability Questionnaire}
This questions need to be reworded to make them as open ended as possible\\
source \url{https://www.usabilitest.com/sus-pdf-generator}- 20-29
\begin {enumerate}
\item Overall, I am satisfied with how easy it is to use this system.
\item It was simple to use this system.
\item I could effectively complete the tasks and scenarios using this system.
\item I was able to complete the tasks and scenarios quickly using this system.
\item I was able to efficiently complete the tasks and scenarios using this system.
\item I felt comfortable using this system.
\item It was easy to learn to use this system.
\item I believe I could become productive quickly using this system.
\item The system gave error messages that clearly told me how to fix problems.
\item Whenever I made a mistake using the system, I could recover easily and quickly.
\item The information (such as online help, on-screen messages, and other documentation) provided with this system was clear.
\item It was easy to find the information I needed.
\item The information provided for the system was easy to understand.
\item The information was effective in helping me complete the tasks and scenarios.
\item The organization of information on the system screens was clear.
\item The interface of this system was pleasant.
\item I liked using the interface of this system.
\item This system has all the functions and capabilities I expect it to have.
\item Overall, I am satisfied with this system.
\item I think that I would like to use this system frequently.
\item I found the system unnecessarily complex.
\item I thought the system was easy to use.
\item I think that I would need the support of a technical person to be able to use this system.
\item I found the various functions in this system were well integrated.
\item I thought there was too much inconsistency in this system.
\item I would imagine that most people would learn to use this system very quickly.
\item I found the system very cumbersome to use.
\item I felt very confident using the system.
\item I needed to learn a lot of things before I could get going with this system.
\item \textbf{The below were added to this list by Olu based on Nielson's Heuristics}
\item The software provided me system's current state and what actions can be done or where to go or what change was made.
\item I was able reuse a previously defined value without having to memorize or jot it.
\item I was able to reverse an error and didn't have to restart a task due to error.
\item I was able to refer to help/documentation easily when I needed it.
\item I was pre-warned of errors based on the actions I performed
\end {enumerate}
\section{Analytic Hierarchy Process}

>>>>

\subsection{Task selection criteria}
**The task selection will be determined with the aid of the domain expert attached to any of the selected projects.\\ 
**The domain expert will be asked to consider the below criteria when defining a task. \\
**Domain experts will also be asked to identify what background knowledge is necessary for the suggested tasks - Novice, Intermediate, Advanced
\begin {enumerate}
\item Collectively all tasks should not take no more than 2 hours.
\item Selected tasks should reflect common use cases of  the software.
\item Include tasks that require a set of sequential or hierarchical steps to be completed

\end {enumerate}

\subsection{Usability Questionnaire}
Two sources of standardized usability questionnaire we could use.

- \url{https://www.usabilitest.com/sus-pdf-generator}- 20-29 - SUS.\\
- \url{https://uiuxtrend.com/pssuq-post-study-system-usability-questionnaire/} - PSSUQ

\section{Analytic Hierarchy Process}
